On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-07-15 paper_lap/JCP_response1/05apparatus.tex
updating response and manuscript

\section{Numerical apparatus \label{sec:napp}}
\subsection{Adjoint discretization}
\upd{Let $X = \mathbb{L}^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{X},\left< \cdot, \cdot \right>_{\underline{X}}$
denote the standard inner products on the Hilbert spaces $X,$ and $\underline{X}$ respectively.
The following lemma relates the discretization of the inverse of an operator to the adjoint of the discretization of its inverse. Its proof follows directly from the definition of the adjoint and is omitted.

\begin{lemma}\label{lem_adjm}
Suppose $A: X \to X$ is a bounded invertible operator and that $\uA: \uX \to \uX$ is the corresponding discretized operator such that
\begin{align}
\left| \langle f,A^{-1} g \rangle_{X} - \langle S[f],\uA^{-1} S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X},
\end{align}
for all $f$ and $g$ in some subspace $Y \subset L^2([0,L]).$  Then, for all functions $f$ and $g$ in $Y$
\begin{align}
\left| \langle f,(A^{-1})^* g \rangle_{X} - \langle S[f],\left(A^{-1}_\epsilon\right)^T S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X}
\end{align}
where $\,{{}^*}\,$ denotes the adjoint.
\end{lemma}
}

@@

For a panel $\gamma([s_1,s_2])$ with discretization nodes \upd{$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ In~\cref{sec:appb}, we show that the interpolation error in the density
at panels away from the corner is related to the interpolation error in the solution to a related Dirichlet boundary value problem.
{\color{red}
Typically we use 16th order Gauss-Legendre panels and choose their sizes so that their length is no more than their distance to the nearest corner. This latter choice guarantees that for any $\epsilon>0$ there exists an $M$ such that if the Gauss-Legendre panels are discretized using an $M$-point Gauss-Legendre rule then the density on that panel can be interpolated to relative precision $\epsilon$ in an $L^2$-sense.
(we discuss a sketch of a proof in~\cref{sec:appb})}.

@@

We begin with the following proposition, the proof of which follows immediately from the definition of the kernel $k$ and is omitted.
\begin{proposition}\label{prop_hanalytic}
Suppose that $f$ is a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (\upd{\uA}^T)^{-1} \upd{\uf}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation. Further suppose that the discretization nodes are ordered so that $s_1,\dots,s_P$ correspond to the corner panel associated with the interval $(-\delta,\delta),$ $s_{P+1},\dots,s_{P+M}$ correspond to the Gauss-Legendre panel immediately to the left associated with the interval $(-2\delta,-\delta),$ and $s_{P+M+1},\dots,s_{P+2M}$ to the Gauss-Legendre panel immediately to the right associated with the interval $(\delta,2\delta).$
Then
\begin{align}\label{eqn:def_hfun}
h(t) = \sum_{i=P+2M+1}^N k(s_i,t) \sqrt{w_i} \,\underline{\sigma}_i
\end{align}
is an analytic function of $t$ for all $t \in (-2\delta,2\delta).$
\end{proposition}

@@

\upd{
\begin{remark}
Though the above method produces a viable method for reducing the problem, as written the reduction appears to be non-local --- in order to compute the right-hand side of the subproblem one must evaluate contributions from the rest of the domain. In fact, the values of $\underline{f}_0$ can be obtained using only local information. Specifically, we observe that
\begin{align}
\left(h(s_i) \sqrt{w_1}, \dots, h(s_{P+2M}) \sqrt{w_{P+2M}}\right)^T =& \left(f(s_i) \sqrt{w_1}, \dots, f(s_{P+2M}) \sqrt{w_{P+2M}}\right)^T-\\
& \underline{A}_{\rm red}^T \left(\sigma_1 \sqrt{w}_1,\dots, \sigma_{P+2M} \sqrt{w_{P+2M}}\right)^T,
\end{align}
where $\underline{A}_{\rm red}$ is the submatrix of $\underline{A}$ corresponding to the first $P+2M$ rows and columns. Since $h$ is analytic on $(-2\delta,2 \delta),$ $h(t)$ can be accurately approximated for any $-2\delta<t<2\delta$ by interpolation from its values at the nodes $s_1,\dots,s_{P+2M}.$
\end{remark}}

>>>>

\section{Numerical apparatus \label{sec:napp}}
\subsection{Adjoint discretization}
\upd{Let $X = L^2([0,L])$ and $\underline{X} = \mathbb{R}^{N}$.  Let $\left< \cdot, \cdot \right>_{X},\left< \cdot, \cdot \right>_{\underline{X}}$
denote the standard inner products on the Hilbert spaces $X,$ and $\underline{X}$ respectively.
The following lemma relates the discretization of the inverse of an operator to the adjoint of the discretization of its inverse. Its proof follows directly from the definition of the adjoint and is omitted.

\begin{lemma}\label{lem_adjm}
Suppose $A: X \to X$ is a bounded invertible operator and that $\uA: \uX \to \uX$ is the corresponding discretized operator such that
\begin{align}
\left| \langle f,A^{-1} g \rangle_{X} - \langle S[f],\uA^{-1} S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X},
\end{align}
for all $f$ and $g$ in some subspace $Y \subset L^2([0,L]).$  Then, for all functions $f$ and $g$ in $Y$
\begin{align}
\left| \langle f,(A^{-1})^T g \rangle_{X} - \langle S[f],\left(A^{-1}_\epsilon\right)^T S[g] \rangle_{\uX} \right| \le \epsilon \|f\|_{X} \|g\|_{X}
\end{align}
where $\,{{}^T}\,$ denotes the adjoint.
\end{lemma}
}

@@

For a panel $\gamma([s_1,s_2])$ with discretization nodes \upd{$x_i,\dots,x_{i+M-1}$} corresponding to a Gauss-Legendre panel the density is smooth and thus it is expected to be well-represented in the basis of Legendre polynomials (shifted and scaled to the interval $[s_1,s_2]$). Hence standard interpolation techniques can be used to obtain an accurate approximation to the density $\sigma$ on the interval $s_1 \le s\le s_2.$ \upd{In~\cref{sec:appb}, we show that the interpolation error in the density
at panels away from the corner is related to the interpolation error in the solution to a related Dirichlet boundary value problem.}

@@

We begin with the following proposition, the proof of which follows immediately from the definition of the kernel $k$ and is omitted.
\begin{proposition}\label{prop_hanalytic}
Suppose that $f$ is a piecewise-analytic function in $S_\epsilon$ and  $\underline{\sigma} = (\upd{\uA}^T)^{-1} \upd{\uf}$ is the approximation to the Neumann density obtained using the adjoint of the discretization for the interior Dirichlet boundary integral equation. Further suppose that the discretization nodes are ordered so that $x_1,\dots,x_{2K}$ correspond to the corner panel associated with the interval $(-\delta,\delta),$ $x_{2K+1},\dots,x_{2K+M}$ correspond to the Gauss-Legendre panel immediately to the left associated with the interval $(-2\delta,-\delta),$ and $x_{2K+M+1},\dots,x_{2K+2M}$ to the Gauss-Legendre panel immediately to the right associated with the interval $(\delta,2\delta).$
Then
\begin{align}\label{eqn:def_hfun}
h(t) = \sum_{i=2K+2M+1}^N k(x_i,t) \sqrt{w_i} \,\underline{\sigma}_i
\end{align}
is an analytic function of $t$ for all $t \in (-2\delta,2\delta).$
\end{proposition}

@@

\upd{
\begin{remark}
Though the above method produces a viable method for reducing the problem, as written the reduction appears to be non-local --- in order to compute the right-hand side of the subproblem one must evaluate contributions from the rest of the domain. In fact, the values of $\underline{f}_0$ can be obtained using only local information. Specifically, we observe that
\begin{align}
\left(h(x_i) \sqrt{w_1}, \dots, h(x_{2K+2M}) \sqrt{w_{2K+2M}}\right)^T =& \left(f(k_i) \sqrt{w_1}, \dots, f(k_{2K+2M}) \sqrt{w_{2K+2M}}\right)^T-\\
& \underline{A}_{\rm red}^T \left(\sigma_1 \sqrt{w}_1,\dots, \sigma_{2K+2M} \sqrt{w_{2K+2M}}\right)^T,
\end{align}
where $\underline{A}_{\rm red}$ is the submatrix of $\underline{A}$ corresponding to the first $2K+2M$ rows and columns. Since $h$ is analytic on $(-2\delta,2 \delta),$ $h(t)$ can be accurately approximated for any $-2\delta<t<2\delta$ by interpolation from its values at the nodes $x_1,\dots,x_{2K+2M}.$
\end{remark}}

### 2020-07-15 paper_lap/JCP_response1/manuscript.tex
updating response and manuscript

\documentclass[12pt,times]{elsarticle}
\usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
\usepackage[margin=1in]{geometry}
\usepackage{graphics}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{conjecture}{Conjecture}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{corollary}{Corollary}[section]
\newcommand{\beqn}{\begin{equation}}
\newcommand{\eeqn}{\end{equation}}
\newcommand{\psub}{\mbox{$\ddot{-}$}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\sgn}{{\rm sgn}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\bS}{\mathbb{S}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cF}{\overline{\bf F}}
\newcommand{\cU}{\overline{\bf U}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\bP}{{\bf P}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bq}{{\bf q}}
\newcommand{\bv}{{\bf v}}
\newcommand{\bu}{{\bf u}}
\newcommand{\boldf}{{\bf f}}
\newcommand{\bphi}{{\boldsymbol \phi}}
\newcommand{\bmu}{{\boldsymbol \mu}}
\newcommand{\brho}{{\boldsymbol \rho}}
\newcommand{\bC}{{\bf C}}
\newcommand{\bV}{{\bf V}}
\newcommand{\bU}{{\bf U}}
\newcommand{\bF}{{\bf F}}
\newcommand{\bRes}{{\bf R}}
\newcommand{\bM}{{\bf M}}
\newcommand{\bI}{\mathbb{I}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\bL}{\mathbb{L}}
\newcommand{\bX}{\mathbb{X}}
\newcommand{\bx}{\boldsymbol{x}}
\newcommand{\bnu}{\boldsymbol{\nu}}
\newcommand{\bn}{\boldsymbol{n}}
\newcommand{\by}{\boldsymbol{y}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\bub}{\underbar{b}}
\newcommand{\xmyo}{\sqrt{x^2 + y^2 - 2xy\cos{\pi \alpha}}}
\newcommand{\sina}{\sin{(\pi \alpha)}}
\newcommand{\sqsina}{\sin^{2}{(\pi \alpha)}}
\newcommand{\cosa}{\cos{(\pi \alpha)}}
\newcommand{\sinna}{\sin{(\pi \nu (1-\alpha))}}
\newcommand{\cosna}{\cos{(\pi \nu (1-\alpha))}}
\newcommand{\sinn}{\sin{(\pi \nu)}}
\newcommand{\cosn}{\cos{(\pi \nu)}}
\newcommand{\bbmat}{\begin{bmatrix}}
\newcommand{\ebmat}{\end{bmatrix}}
\newcommand{\dudn}[1]{\frac{\partial u_{#1}}{\partial n}}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{lem}{Lemma}
\newtheorem{rem}{Remark}
\newtheorem{comment}{Remark}

@@

\begin{abstract}
In the present paper we describe a class of algorithms for the solution of Laplace's equation on polygonal domains with Neumann boundary conditions. It is well known that in such cases the solutions have singularities near the corners which poses a challenge for many existing methods. 
If the boundary data is smooth on each edge of the polygon, then in the vicinity of each corner the solution to the corresponding boundary integral equation has an expansion in terms of certain (analytically available) singular powers. Using the known behavior of the solution, universal discretizations have been constructed for the solution of the Dirichlet problem. 
However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for {\color{olive}$\mu \in (-1/2,1/2)$} depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations. Our approach is based on using the discretization for the Dirichlet problem in order to compute a solution in the ``weak sense'' by solving an adjoint linear system; namely, it can be used to compute inner products with smooth functions accurately, but it cannot be interpolated.  Furthermore we present a procedure to obtain accurate solutions arbitrarily close to the corner, by solving a sequence of small local subproblems in the vicinity of that corner. The results are illustrated with several numerical examples.
\end{abstract}

@@

\appendix
\section{Approximation of data on corner panels for re-solve}
Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.{\color{red}  In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$ }

\begin{theorem}
Let $\Gamma$ be the boundary of a polygon and $\bx$ be a vertex. Let $r>0$ be a real number such that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r,$ where $B_R(\bx)$ denotes a ball of radius $R$ centered at $\bx.$ Let $L$ denote the length of\, $\Gamma$ and $\gamma: [-L/2,L/2]\to \Gamma$ be an arclength counterclockwise parameterization of\, $\Gamma$ such that $\gamma(0) = \bx.$ Finally, for any $f \in L^2(\Gamma),$ let $H:[0,r] \to \mathbb{R}$ be the function defined by
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(\gamma(s))\,{\rm d}s.
\end{align}
Then $H$ is analytic in a neighborhood of $0$ with Taylor series coefficients $\{ a_n\}$ satisfying
\begin{align}
|a_n| \le \frac{\sqrt{L}}{2^nr^{n+1}} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{theorem}
\begin{proof}
Without loss of generality we can assume that $\Gamma$ is shifted, oriented and parameterized so that $\bx = \gamma(0)= 0$ and the leg of the wedge corresponding to positive $t$ is oriented along the positive $x$ axis. Then
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(s)\,{\rm d}s = \int_{\Gamma\backslash B_{2r}(\bx)} \frac{y(s)}{(t-x(s))^2+y(s)^2}f(s)\,{\rm d}s.
\end{align}
Since $\|\gamma(s)-\gamma(t)\| >2r$ it follows that
\begin{align}
H(t) =\int _{\Gamma\backslash B_{2r}(\bx)}\sum {t^n i}\left(\frac{1}{(x(s)+i y(s))^{n+1}}-\frac{1}{(x(s)-i y(s))^{n+1}} \right) f(s)\,{\rm d}s.
\end{align}
In particular, $H$ has a Taylor series about $t=0,$
\begin{align}
\sum_{n=0}^\infty c_n \left(\frac{t}{2r}\right)^n
\end{align}
where
\begin{align}
|c_n| \le  \frac{\sqrt{L}}{r} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{proof}

@@

But first, we present a lemma about the accuracy of Gaussian quadrature
\begin{lem}
\label{lem:b1}
Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $\mathbb{L}^{2}[-1,1]$, then the integral
$\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
As a consequence, For any $g$ in $\mathbb{L}^{2}(\Gamma)$, then 
\begin{equation}
\left<h_{i},g \right>_{X} = \left< S[h_{i}], S[g] \right>_{\uX}
\end{equation}
\end{lem}

@@

\begin{lem}
\label{lem:b2}
Let $f_{i}$ be given by
\begin{equation}
f_{i}(s) = -2 \int_{s_{1}}^{s_{2}} k(s,t) h_{i}(t) dt \, , s\in [0,L] \setminus V \, . \label{eq:deff}
\end{equation}
Consider the interior Dirichlet problem with boundary data $f_{i}$, where we represent the solution via a double layer potential with density $\sigma_{D,i}$, i.e. $\sigma_{D,i}$ satisfies the integral equation
\begin{equation}
A[\sigma_{D,i}] = -\sigma_{D,i}/2 + \int_{0}^{L} k(s,t) \sigma_{D,i}(t) dt  = f_{i}(s) \, , s\in [0,L] \setminus V \, . 
\end{equation}
Then,
\begin{equation}
\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX} = 
\left< g, \sigma_{D,i} \right> - \left< S[g], \usigma_{D,i} \right>_{\uX}
\end{equation}
\end{lem}

@@

\Cref{lem:b2} shows that the error in evaluating the inner product of the computed density $\usigma$ with a polynomial on
$\Gamma_{\ell}$ is the same as the error in evaluating the inner product of a computed density for a Dirichlet problem $\usigma_{D,i}$ with boundary data $g$. 
The Dirichlet boundary data $f_{i}$ (\cref{eq:deff}) corresponding to the density $\sigma_{D,i}$ is an analytic function on each of the edges of the polygon. 
The discretization of $A$ in~\cite{hoskins2019numerical} is precisely designed to compute $\sigma_{D,i}$ accurately to any desired tolerance, under sufficient refinement of the discretization. Since $g$ is also a smooth function, given a tolerance $\varepsilon$, there exists a sufficiently fine discretization of the boundary such that
\begin{equation}
\left| \left< g, \sigma_{D,i} \right>_{X} - \left< S[g], \usigma_{D,i} \right>_{\uX} \right| < \varepsilon \, . \label{eq:dest}
\end{equation}
In practice, a discretization with macroscopic panels at the corner, panels not at a corner vertex separated from the corner by their panel length, and which resolves $g$ to precision $\varepsilon$ is often sufficient to guarantee~\cref{eq:dest}. 
\begin{rem}
The size of the panel at the corner needs to be chosen based on the angle formed at the corner---smaller panels for angles closer to $0$ or $2\pi$, in order to resolve the corresponding close to touching interactions.
\end{rem}
}

>>>>

\documentclass[12pt,times]{elsarticle}
\usepackage{amsmath,amsthm,amssymb,amscd,fancybox,epsfig,float,subfigure}
\usepackage[margin=1in]{geometry}
\usepackage{graphics}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\newtheorem{definition}{Definition}
\newtheorem{remark}[definition]{Remark}
\newtheorem{conjecture}[definition]{Conjecture}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{corollary}[definition]{Corollary}
\newcommand{\beqn}{\begin{equation}}
\newcommand{\eeqn}{\end{equation}}
\newcommand{\psub}{\mbox{$\ddot{-}$}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\sgn}{{\rm sgn}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\bS}{\mathbb{S}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cF}{\overline{\bf F}}
\newcommand{\cU}{\overline{\bf U}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\bP}{{\bf P}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bq}{{\bf q}}
\newcommand{\bv}{{\bf v}}
\newcommand{\bu}{{\bf u}}
\newcommand{\boldf}{{\bf f}}
\newcommand{\bphi}{{\boldsymbol \phi}}
\newcommand{\bmu}{{\boldsymbol \mu}}
\newcommand{\brho}{{\boldsymbol \rho}}
\newcommand{\bC}{{\bf C}}
\newcommand{\bV}{{\bf V}}
\newcommand{\bU}{{\bf U}}
\newcommand{\bF}{{\bf F}}
\newcommand{\bRes}{{\bf R}}
\newcommand{\bM}{{\bf M}}
\newcommand{\bI}{\mathbb{I}}
\newcommand{\bN}{\mathbb{N}}
\newcommand{\bL}{\mathbb{L}}
\newcommand{\bX}{\mathbb{X}}
\newcommand{\bx}{\boldsymbol{x}}
\newcommand{\bnu}{\boldsymbol{\nu}}
\newcommand{\bn}{\boldsymbol{n}}
\newcommand{\by}{\boldsymbol{y}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\bub}{\underbar{b}}
\newcommand{\xmyo}{\sqrt{x^2 + y^2 - 2xy\cos{\pi \alpha}}}
\newcommand{\sina}{\sin{(\pi \alpha)}}
\newcommand{\sqsina}{\sin^{2}{(\pi \alpha)}}
\newcommand{\cosa}{\cos{(\pi \alpha)}}
\newcommand{\sinna}{\sin{(\pi \nu (1-\alpha))}}
\newcommand{\cosna}{\cos{(\pi \nu (1-\alpha))}}
\newcommand{\sinn}{\sin{(\pi \nu)}}
\newcommand{\cosn}{\cos{(\pi \nu)}}
\newcommand{\bbmat}{\begin{bmatrix}}
\newcommand{\ebmat}{\end{bmatrix}}
\newcommand{\dudn}[1]{\frac{\partial u_{#1}}{\partial n}}

@@

\newtheorem{theorem}[definition]{Theorem}
\newtheorem{lemma}[definition]{Lemma}

@@

\begin{abstract}
In the present paper we describe a class of algorithms for the solution of Laplace's equation on polygonal domains with Neumann boundary conditions. It is well known that in such cases the solutions have singularities near the corners which poses a challenge for many existing methods. 
If the boundary data is smooth on each edge of the polygon, then in the vicinity of each corner the solution to the corresponding boundary integral equation has an expansion in terms of certain (analytically available) singular powers. Using the known behavior of the solution, universal discretizations have been constructed for the solution of the Dirichlet problem. 
However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for \upd{$\mu \in (-1/2,1/2)$} depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations. Our approach is based on using the discretization for the Dirichlet problem in order to compute a solution in the ``weak sense'' by solving an adjoint linear system; namely, it can be used to compute inner products with smooth functions accurately, but it cannot be interpolated.  Furthermore we present a procedure to obtain accurate solutions arbitrarily close to the corner, by solving a sequence of small local subproblems in the vicinity of that corner. The results are illustrated with several numerical examples.
\end{abstract}

@@

\appendix
\section{Approximation of data on corner panels for re-solve}
Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.
\begin{theorem}
Let $\Gamma$ be the boundary of a polygon and $\bx$ be a vertex. Let $r>0$ be a real number such that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r,$ where $B_R(\bx)$ denotes a ball of radius $R$ centered at $\bx.$ Let $L$ denote the length of\, $\Gamma$ and $\gamma: [-L/2,L/2]\to \Gamma$ be an arclength counterclockwise parameterization of\, $\Gamma$ such that $\gamma(0) = \bx.$ Finally, for any $f \in L^2(\Gamma),$ let $H:[0,r] \to \mathbb{R}$ be the function defined by
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(\gamma(s))\,{\rm d}s.
\end{align}
Then $H$ is analytic in a neighborhood of $0$ with Taylor series coefficients $\{ a_n\}$ satisfying
\begin{align}
|a_n| \le \frac{\sqrt{L}}{2^nr^{n+1}} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{theorem}
\begin{proof}
Without loss of generality we can assume that $\Gamma$ is shifted, oriented and parameterized so that $\bx = \gamma(0)= 0$ and the leg of the wedge corresponding to positive $t$ is oriented along the positive $x$ axis. Then
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(s)\,{\rm d}s = \int_{\Gamma\backslash B_{2r}(\bx)} \frac{y(s)}{(t-x(s))^2+y(s)^2}f(s)\,{\rm d}s.
\end{align}
Since $\|\gamma(s)-\gamma(t)\| >2r$ it follows that
\begin{align}
H(t) =\int _{\Gamma\backslash B_{2r}(\bx)}\sum {t^n i}\left(\frac{1}{(x(s)+i y(s))^{n+1}}-\frac{1}{(x(s)-i y(s))^{n+1}} \right) f(s)\,{\rm d}s.
\end{align}
In particular, $H$ has a Taylor series about $t=0,$
\begin{align}
\sum_{n=0}^\infty c_n \left(\frac{t}{2r}\right)^n
\end{align}
where
\begin{align}
|c_n| \le  \frac{\sqrt{L}}{r} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{proof}

@@

But first, we present a lemma about the accuracy of Gaussian quadrature
\begin{lemma}
\label{lem:b1}
Suppose that $p$ is a polynomial of degree less than $M$, then for any function $g$ in $\mathbb{L}^{2}[-1,1]$, then the integral
$\int_{-1}^{1} p \cdot g$ can be computed accurately using Gaussian quadrature of any order greater than or equal to $M$.
As a consequence, For any $g$ in $\mathbb{L}^{2}(\Gamma)$, then 
\begin{equation}
\left<h_{i},g \right>_{X} = \left< S[h_{i}], S[g] \right>_{\uX}
\end{equation}
\end{lemma}

@@

\begin{lemma}
\label{lem:b2}
Let $f_{i}$ be given by
\begin{equation}
f_{i}(s) = -2 \int_{s_{1}}^{s_{2}} k(s,t) h_{i}(t) dt \, , s\in [0,L] \setminus V \, . \label{eq:deff}
\end{equation}
Consider the interior Dirichlet problem with boundary data $f_{i}$, where we represent the solution via a double layer potential with density $\sigma_{D,i}$, i.e. $\sigma_{D,i}$ satisfies the integral equation
\begin{equation}
A[\sigma_{D,i}] = -\sigma_{D,i}/2 + \int_{0}^{L} k(s,t) \sigma_{D,i}(t) dt  = f_{i}(s) \, , s\in [0,L] \setminus V \, . 
\end{equation}
Then,
\begin{equation}
\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX} = 
\left< g, \sigma_{D,i} \right> - \left< S[g], \usigma_{D,i} \right>_{\uX}
\end{equation}
\end{lemma}

@@

\Cref{lem:b2} shows that the error in evaluating the inner product of the computed density $\usigma$ with a polynomial on
$\Gamma_{\ell}$ is the same as the error in evaluating the inner product of a computed density for a Dirichlet problem $\usigma_{D,i}$ with boundary data $g$. 
The Dirichlet boundary data $f_{i}$ (\cref{eq:deff}) corresponding to the density $\sigma_{D,i}$ is an analytic function on each of the edges of the polygon. 
The discretization of $A$ in~\cite{hoskins2019numerical} is precisely designed to compute $\sigma_{D,i}$ accurately to any desired tolerance, under sufficient refinement of the discretization. Since $g$ is also a smooth function, given a tolerance $\varepsilon$, there exists a sufficiently fine discretization of the boundary such that
\begin{equation}
\left| \left< g, \sigma_{D,i} \right>_{X} - \left< S[g], \usigma_{D,i} \right>_{\uX} \right| < \varepsilon \, . \label{eq:dest}
\end{equation}
In practice, a discretization with macroscopic panels at the corner, panels not at a corner vertex separated from the corner by their panel length, and which resolves $g$ to precision $\varepsilon$ is often sufficient to guarantee~\cref{eq:dest}. 
\begin{remark}
The size of the panel at the corner needs to be chosen based on the angle formed at the corner---smaller panels for angles closer to $0$ or $2\pi$, in order to resolve the corresponding close to touching interactions.
\end{remark}
}
